\clearpage
\appendix
\onecolumn

\section{Description of the demonstrated system}
\label{sec:desc-sup}
% description of the demo system
The demonstrated system comprises two components, i.e. the server side and client side.
At the server side, a set of travel routes are generated from a trained structured SVMs as well as 
a query sent by the client. 
The generated routes are then sent to the client, which runs in a web browser, to visualise.
The server side was written in the Python programming language using \textit{pystruct}~\cite{JMLR:v15:mueller14a},
a Python library for structured learning and prediction,
as well as other essential Python libraries (with details below).
The client side was written in HTML, JavaScript and CSS.


% required setup
% website for users
\subsection{System setup}
\label{ssec:setup}
We created a website for users to try this system, it can be accessed at \url{http://115.146.87.43:8080/}.
As the source code of this system is hosted in a public GitHub repository, 
anyone interested in it can also run the system locally, by following the steps below:
\begin{enumerate}
\item Download the source code of the system from \url{https://github.com/cdawei/path_vis} 
% DW: move this to https://github.com/computationalmedia if it gets accepted?
\item Install the Python runtime and required libraries: 
      \begin{itemize}
      \item \textit{Python} version 3.5.3
      \item \textit{numpy} version 1.12.1 or newer
      \item \textit{scipy} version 0.19.0 or newer
      \item \textit{pandas} version 0.19.2
      \item \textit{scikit-learn} version 0.18.1 or newer
      \item \textit{joblib} version 0.11 or newer
      \item \textit{pystruct} version 0.2.4 or newer
      \end{itemize}
\item Go to the directory with system source code and launch the server slide: \texttt{python server.py}
\item Access \url{http://localhost:8080} using a web browser to use the visualisation system.
\end{enumerate}


%information about the presenters, including the relationship to the project
\subsection{Presenter}
\label{ssec:presenter}
The demonstrated system will be presented by Dawei Chen, a second year PhD student at the Australian National University.
The presenter is one of the member in a group that working on this project.
